% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Xiaolong Ma}

\basicInfo{
  \email{mxl.m@qq.com} \textperiodcentered\ 
  \phone{(+86) 15600519843} \textperiodcentered\ 
\github[DragonFive]{https://github.com/DragonFive}}
%  \linkedin[billryan8]{https://www.linkedin.com/in/billryan8}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{ Institute of Computing Technology(ICT,CAS)}, Beijing, China}{2015 -- Present}
\textit{Master student} in computer vision/deeplearning (CV/DL), expected June 2018
\datedsubsection{\textbf{Xidian University}, Shaanxi, China}{2011 -- 2015}
\textit{B.S.} in Software Engineering-Embedded system

\section{\faUsers\ Intern Experience}
\datedsubsection{\textbf{sensetime} Beijing, China}{Apr.2017 -- Present}
\role{algorithm researcher Intern}{Department: algorithm platform}
develop the deeplearning framework-sensenet,and deploy it on Virtualization  platform.
\begin{itemize}
  \item Implemented some forward and backward of layers in sensenet.
  \item Deployed the sensenet and tensorflow on k8s platform, monitor the resources and train network in parallel.
  \item tools:caffe,tensorflow,k8s,docker,slurm,openmpi,intelmpi,HIG etc.
\end{itemize}


\datedsubsection{\textbf{Ricoh} Beijing, China}{Mar.20116 -- Sept.2016}
\role{computer vision Intern}{Department: video algorithm research}
develop the video synopsis system for the video from street.
\begin{itemize}
  \item Implemented the video synopsis system, compressed the video to 1/24 and the object seach engine.
  \item Improved the core algorithm by 900 times by the way of cache and multi-threads.
\end{itemize}

\section{\faCogs\ Project Experience}
\datedsubsection{\textbf{physical side video monitor Projects}}{Oct.2016 -- Mar.2017}
\role{algorithm researcher}{}
Built a video monitor system,detect and track the moving object in video, store and search the object.
\begin{itemize}
  \item Designed the combination feature and Bow model to store and search the object.
  \item Study,implement or imporve the algorithm of MDNet,GoTurn,TLD,KCF,etc.
\end{itemize}

\datedsubsection{\textbf{ Boat detection and matching}}{May. 2015 -- Present}
\role{ coder and designer}{}
Detecting the boat on the sea in photo,Counting the number of boat in the video.
\begin{itemize}
  \item Using the SIFT to match photo,make the boat data set,using Gaussian mixed model to locate boat in video.
  \item Using svm+hog,adaboost+harr and DPM+hog to detect boat in static image.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{2} Prize(2/90)}, Award on CCF National Youth Big Data Contest }{Dec. 2015}
\datedline{\textit{\nth{2} Prize}, Award on Spark Cup Software Contest }{Nov. 2014}
\datedline{\textit{\nth{1} Prize(11/540)}, Award on Huawei Cup Coding Contest }{Jun. 2013}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: https://dragonfive.github.io/
  \item familiar with c++/python,opencv/caffe/tensorflow/keras,k8s/docker
  \item familiar with computer vision,machine learning,deep learning algorithm.
  \item Implementation of algorithm: https://github.com/DragonFive/python\_cv\_AI\_ML
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
